Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-26 paper/main.tex

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus, and overall
eight $t$-contrast for the audio-description stimulus
(Tab.~\ref{tab:contrasts}).
% how
Contrasts differ in contrasted categeories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can found at NeuroVault
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
Reliably across all five movie contrasts, we find bilaterally significant
clusters that overlap with the PPA group overlap
(Fig.~\ref{fig:stability-slices}).
% AV: RSC & LOC
Results of the movie also yielded significant clusters in the ventral precuneal
cortex and posterior cingulate gyrus (i.e. retrosplenial complex; contrasts 1,
4, 5), and lateral occipital cortex (contrasts 1, 2, 4, 5).

@@

% AD: results
In results from the analysis of the audio-description, all contrasts except
contrast 7 (\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and
contrast 8 (\texttt{se\_new} > non-spatial categories) yielded significant
bilateral clusters in anterior regions of the group PPA overlap
(Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
Results from the analysis of the audio-description also yielded bilaterally
significant clusters in the ventral precuneus (all contrasts except contrasts 8)
and lateral occipital cortex (bilateral in contrasts 1 to 4; unilateral in
contrasts 6 and 7).
% concluding stament regarding PPA, RSC, and LOC
The results across the contrasts of the movie and audio-description indicate
that our findings regarding the PPA but also RSC and LOC are robust and do not
depend on the design of one specific contrasts.
% but:
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} >
\texttt{se\_old}) that used the most heterogeneous categories comprising the
least amount of events yielded neither a significant cluster in the
right-hemispheric nor left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

>>>>

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
audio-description (Tab.~\ref{tab:contrasts}).
% how
Contrasts differ in contrasted categories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
Reliably across all five movie contrasts, we find bilaterally significant
clusters that overlap with the PPA group overlap
(Fig.~\ref{fig:stability-slices}).
% AV: RSC & LOC
Several contrasts of the movie also yielded bilaterally significant clusters in
the ventral precuneal cortex and posterior cingulate gyrus (i.e. retrosplenial
complex; contrasts 1, 4, 5), and lateral occipital cortex (contrasts 1, 2, 4,
5).

@@

% AD: results
In results from the analysis of the audio-description, all contrasts except
contrast 7 and 8  yielded significant bilateral clusters in anterior regions of
the group PPA overlap (Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
Contrasts of the audio-description also yielded bilaterally significant clusters
in the ventral precuneus (all contrasts except contrasts 8) and lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7).
% concluding stament regarding PPA, RSC, and LOC
Results across contrasts of both naturalistic stimuli indicate that our findings
regarding the PPA but also RSC and LOC are robust and do not depend on the
design of one specific contrasts.
% but:
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 7 and 8 (\texttt{se\_new}, \texttt{se\_old} > non-spatial
categories, and \texttt{se\_new} > non-spatial categories) that used the most
heterogeneous categories (nouns indicating switches to other settings) and a low
amount of events yielded neither a significant cluster in the right-hemispheric
nor left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.
